Supplementary Information

### 2015-06-25 manuscript/coverletter.tex
one more tiny change

In general, we found little evidence of an effect of latitude on the
relationship between specialisation and species richness, implying that
latitudinal variation in food-web structure may be driven purely by
latitudinal gradients in species richness. If diet breadth may be taken as a
measure of a species' Eltonian (biotic) niche, this means that our results are
food webs do not conform to the latitude-niche-breadth hypothesis. Ecosystem
type, on the other hand, had a greater impact on scaling exponents, suggesting
that different processes may structure food webs in different habitats.
Indeed, freshwater food webs departed from the overall trend and showed strong
effects of latitude on scaling relationships. Only in these food webs was the
latitude-niche-breadth hypothesis.

>>>>

In general, we found little evidence of an effect of latitude on the
relationship between specialisation and species richness, implying that
latitudinal variation in food-web structure may be driven purely by
latitudinal gradients in species richness. If diet breadth may be taken as a
measure of a species' Eltonian (biotic) niche, this means that food webs
in general do not conform to the latitude-niche-breadth hypothesis. Ecosystem
type, on the other hand, had a greater impact on scaling exponents, suggesting
that different processes may structure food webs in different habitats.
Indeed, freshwater food webs departed from the overall trend and showed strong
effects of latitude on scaling relationships. Only in these food webs was the
latitude-niche-breadth hypothesis.
